\documentclass{report} % was article, thought i'd try with report...
\usepackage{float}
%\usepackage{fullpage} % 1 inch margins
%\usepackage{harvard} % harvard reference style++
\usepackage[hidelinks]{hyperref} % do not remember entirely what this does
%%\usepackage{minted} % [LINUXONLY] list environment with code highlighting

\title{Object oriented systems engineering \\ IMT3102 \\ Portfolio 1}
\author{Martin Kristian Mellum  \\ Thomas Sigurdsen 090320} % enter student number
\date{\today}

\begin{document}
\maketitle       % make title
%%\section{Abstract} % not sure if needed
%%This section is to be written when all else is done. 100-200 words summarizing.
\tableofcontents % make table of contents
\pagebreak	% and break the page, because pretty

\section{Introduction} % not sure if needed
In this first portfolio we will pick 3 - 4 open-source projects. We are going to analyze each of them from a software engineering point of view. Delve into the differences of infrastructure, communication, openness, financial and social aspects of the open-source development model for these projects. Much of this analysis will be done using chapter 3 of Karl Fogel's Producing Open Source Software\cite{kfposs} as a lense.

The projects we have initially chosen are:
\begin{itemize}
\item Media Player Classic\cite{mpcweb}
\item Ez publish\cite{ezpubweb}
\item OpenDungeons\cite{odweb} % I think we should drop this, pick a new better one, and write up a bit on the curiosa on this one.
\end{itemize}
It was quickly discovered during the research period of this report, that OpenDungeons was inadequate. The reasons for this is that it is rather small, it is in a pre alpha stage, and has only a small pack of contributors. It will stand and be used as an example and used in the comparison, but no more analysis than this will be done. We picked instead to focus on Boost\cite{boostweb}, a c++ library collection, as our third project for this report.

\section{Project introduction}
\subsection{Media Player Classic}
Media Player Classic (MPC) is a minimalistic media player. They try to keep the old and simple look that the Windows Media Player 6.4 had, which was released in 1999. Although, behind the old look it has most of the features that new media player comes with, including codecs to play new formats. 
This is also what they say about their player on their front page:
\begin{quote}
MPC-HC is an extremely light-weight media player for Windows.
The player supports all common video and audio file formats available for playback.\cite{mpcweb}
\end{quote}
As you can see, it stands MPC-HC, and this is a fork of the original MPC. This "HC" version is the one that their adding new features to, along with fixing bugs and libraries. The original MPC was just intended to be the same Classic Player with no more features, and just fixing bugs and updating libraries, but after the leader, Gabest didn't had more time for the project, the project is inactive. %Or more likely dead
Gabest was the main developer and the leader of the MPC project, it started as a closed-source project. Later they did make an open source project out of it.
The MPC-HC is mainly written in C++, 87 percent of the code are written in C++, and 11 percent in C\cite{ohlohmpc}. They have also done a lot of decreasing code lines. By taking a look at the graph named "Lines of Code" on mpc-hc page at ohloh.net\cite{ohlohmpc} you can see that they have went from maximum 616 000 lines of code in April 2010. To 168 000 lines of code September 2012.
Their page seems also very open, and it's easy to see that it's an open source project. You have easy access to their changelog, bug reports, about, and development wiki. From the development wiki site you can easy find what you expect to find.
 
\subsection{Ez Publish}
Ez Publish is a http based content management system. It is built using mainly php and effectively uses a dual licensing scheme.

Their about reads as follows:
\begin{quote}
eZ Systems is in the business of Web Content Management Solutions and has been since 1999. We maintain a global presence in Europe, Asia and the Americas. 

Our large international business partner network is the foundation of our success in the market. 

Our team of engineers, consultants and partner managers enables successful implementations for our customers and partners.\cite{ezpubwebabout}
\end{quote}
The Ez Publish website\cite{ezpubweb} appears as a business front-end, and as such can be a bit off putting. There is but one direct mention of open-source, under a "What's in it for you" banner at the top.

Until you find the community portal for Ez Publish, it's all like a big storefront. Mentioning open-source and community in between selling itself. Indeed, running a \url{inurl:"http://ez.publish.no" "share.ez.no"} on google returns no results.

Poking around will let you find the open-source community web page\cite{ezcomweb}

\subsection{OpenDungeons} %% add more info here
\begin{quotation}
OpenDungeons is an open source, real time strategy game sharing game elements with the Dungeon Keeper series and Evil Genius. Players build an underground (or overground) dungeon which is inhabited by creatures. Players fight each other for control of territory by indirectly commanding their creatures, directly casting spells in combat, and luring enemies into sinister traps.\cite{odwebabout}
\end{quotation}

\subsection{Boost}
The Boost effort was started in 1998 by Bernan G. Dawes. He wrote the initial proposal\cite{boostproposal} which in turn has been established as the Boost libraries. The reasoning for the name is best described in the Boost faq\cite{boostfaq}:
\begin{quote}
Boost began with Robert Klarer and I fantasizing about a new library effort over dinner at a C++ committee meeting in Sofia Antipolis, France, in 1998. Robert mentioned that Herb Sutter was working on a spoof proposal for a new language named Booze, which was supposed to be better than Java. Somehow that kicked off the idea of "Boost" as a name. We'd probably had a couple of glasses of good French wine at that point. It was just a working name, but no one ever came up with a replacement. (Beman Dawes)
\end{quote}
The Boost libraries is very much alive, it has become a mature codebase. With several of its libraries put into the newer C++ standards (like C++ Technical Report 1 and C++11).

\section{Licenses}
\subsection{Media Player Classic}
MPC-HCs information about their licensing is easily found in the readme file in the source code\cite{mpcsource}. They are using the GPLv3\cite{gplv3}.
\subsection{Ez Publish}
Ez Publish uses a quinary licensing scheme\cite{ezpubweblicenses}. Most of them are for special use cases, meaning enterprises use the "eZ Business Use License Agreement" while most others use the GPLv2\cite{gplv2}. Information about their licensing and when to use which is more or less hidden.
\subsection{Boost}
Boost is a bit special because many of the contributors is or have been members of the C++ standards committee, as such it is not a project with a lot of idealism for open-source. Rather the reason for it being open-source is more of a standards issue than anything else. The Boost license\cite{boostlicense} was written specifically for The Boost C++ libraries.

\section{Infrastructure}
\subsection{Media Player Classic}
\subsubsection{Mailing Lists}
MPC-HC seems not to use mailing lists too much, it's hard to find on their page. I did in the end find one mailing list, I had to search the page to find it. It's a mailing list for their bug report system, and is used as a notification to subscribers to inform them about tickets in their bug reporting system\cite{mpctracsupport}\cite{mpctracmail}. After long time searching for some mailing lists I went to their irc channel to ask them, and got as I suspected in reply that they don't have any. All communication between the developers happens through the irc channel.  This conflicts to how Karl Fogel is talking about the mailing lists in his book\cite{kfposs}. 
\subsubsection{Version control}
MPC-HC's version control is easily find on the front page\cite{mpcweb} under the news section. It's because they just recently changed it to GitHub. The changed where because it was easier for people to contribute, they say. This message about that they want more contributors goes through the entire page, and is also written much about in the readme\cite{mpcsource}.
\subsubsection{Bug tracker}
The bug tracker their using is the Trac\cite{tracweb} system, and is used to report bugs, feature request, or other kind of requests or changes. It is linked to from several places on their site, and they have also made a guide\cite{mpcbugguide} 
on how to proceed with a ticket ass they call a bug report, or any other report. 
\subsubsection{Instant messaging}
They are using irc channels\cite{mpccontact}, and seems like the main communication between the developers. Though, they only got two channels, one for users, help and such, and one for development channel. If you got some technical questions or something to discuss, it's here you do it. It's not the way Karl Fogel recommend doing things, because you have to be there when it happens to read it, and to learn from it. It also may be harder to get into the project if you're new to the project. On the other hand, the only got 168 000 lines of code\cite{ohlohmpc} at the moment, and have a pretty detailed to-do list\cite{mpctodo}
\subsubsection{Website}
The website I would say is quite easy for a regular user to find what he need, download the software, report bugs, read about the. If you are more interested, or are contributing in the project, and spends some time in the development wiki\cite{mpcwiki} you easy find the things you want. Karl Fogel describes a website like this in his book:\begin{quotation}
(...)it act more as a glue for the other components than as a tool unto itself.\cite{kfposs}
\end{quotation} 
And that it was it does. From the page you can get all the information you need.
\subsection{Ez Publish}
\subsubsection{Mailing Lists}
Ez Publish has mailing lists\cite{ezpubwebmaillists}\footnote{At the first counseling Thomas stated that Ez Publish seemingly did not use mailing lists. It has been discovered that this was indeed false.} divided into 10 categories, half of which is bug related. All of the categories are more or less aimed at development/developers.
\subsubsection{Version control}
Ez Publish uses github\cite{ezpubgithub} as their community/open-source code interface/version control. Here they have lots of public repositories (40 repositories at the 30th of August 2012). They use primarily push requests to receive code from sources other than Ez Publish's own engineers. % this may be false, check mail.
\subsubsection{Bug tracker}
% should say more about how bugs are handled/travel through the system.
Ez Publish uses a bug tracking system from Waterproof Software\cite{waterproofweb} called wIT\cite{waterproofwebwit}. Hosted through the Ez publish platform.
\subsubsection{Instant messaging} % check in mail?
\subsubsection{Coding standards}
\subsubsection{Website}
% I think this fits nicely elsewhere, don't need this subsubsection
All of Ez Publish's websites are hosted on the Ez Publish platform.
\subsubsection{Money}
Ez Publish straightforwardly presents itself as a company making money off of their enterprise support for the Ez Publish platform.

\subsection{Boost}
\subsubsection{Mailing Lists}
Boost offers a range of mailing lists\cite{boostmaillists} for both users and developers. This is the main information channel for the Boost community, or as the mailing lists overview page\cite{boostmaillists} puts it:
\begin{quote}
The mailing lists are the heart of the Boost community.
\end{quote}

\subsubsection{Version control}
Boost uses both Concurrent Versions System or cvs hosted on sorceforge\cite{boostcvssourceforge} and Subversion or svn hoted on the Boost webpage\cite{boostsvn}. The cvs repository is hosted on sourceforge and has a small group of developers with write permission. While the svn ...

\subsubsection{Bug tracker}
The little guide page that is the first step on the way to report a bug, is very much the same ass others. It has a clean step by step guide to tell you what to do. The first steps is as Karl Fogel advices in his book\cite{kfposs}. They tell you check if it is already fixed(like if you have your latest version), then it tells you to search if any others have found the same bug. It doesn't include the step where you shall ask a friend if he can provoke the bug. After this step it tells you where to go to create a new ticket. The bug tracker system their using is the Trac. 

\subsubsection{Instant messaging}
\subsubsection{Website}

\section{Conclusion/Comparison?}

\bibliographystyle{unsrt} % change for dcu, or something else entirely? unsrt is nice
\bibliography{ProjectComparisonRefs}
\end{document}
